Анализ поездок на ж/д транспорте по России

### 2021-12-18 article/article.tex
little fixes

\begin{figure}
	\includegraphics[scale=0.4]{4pict}
	\caption{Прямой связи между количеством свободных мест и стоимости билетов не наблюдается: в одном случае при высвобождении мест билеты подешевели, в другой ситуации при изменении спроса цена не менялась}
\end{figure}

@@

	\item При высоком спросе в ажиотажные даты РЖД добавляет дополнительные вагоны к поездам, причём иногда даже в несколько этапов. Это означает, что если в какой-то момент билетов на более дешёвый поезд или класс вагона нет, то не стоит сразу же покупать более дорогие билеты, а есть смысл подождать, пока РЖД добавит дополнительные вагоны
\end{itemize}
\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

>>>>

\begin{figure}
	\includegraphics[scale=0.4 ]{4pict}
	\caption{Прямой связи между количеством свободных мест и стоимости билетов не наблюдается: в одном случае при высвобождении мест билеты подешевели, в другой ситуации при изменении спроса цена не менялась}
\end{figure}

@@

	\item При высоком спросе в ажиотажные даты РЖД добавляет дополнительные вагоны к поездам, причём иногда даже в несколько этапов. Это означает, что если в какой-то момент билетов на более дешёвый поезд или класс вагона нет, то не стоит сразу же покупать более дорогие билеты, а есть смысл подождать, пока РЖД добавит дополнительные вагоны
\end{itemize}
